Community-Conditioned Language Models

### 2020-10-23 paper/paper.tex
finish drafting analysis section

% Computation of loss/community/model (show all)
\begin{table}
  \centering
  \begin{tabular}{ccc}
    todo &todo &todo 
  \end{tabular}
  \caption{Model losses per community}
  \label{tab:losses}
\end{table}
TODO commentary

TODO: say why we can't use the losses directly!
Turn a CCLM into a community classifier using Bayes theorem: The
probability that a given post $m$ belongs to a community $c_i$ can be
calculated as:
\[P(c=c_i | m) = P(m | c_i)\frac {P(m)} {P(c=c_i)}\]

$P(c=c_i)$ is the frequency of community $c_i$ in the dataset, and
$P(m | c_i)$ is given by the CCLM. $P(m)$ is our normalisation factor, which can be set so that
\[\sum_i P(c=c_i | m) = 1\].

Knowing that $m$ \emph{actually} comes from community $c_j$, we test
the recall and precision abilities of our classifier.  if we let
$C_{ij} = average_{m ∈ Posts(c_j)}(P(c=c_i | m))$ then $C$ is a
confusion matrix for it.

(TODO: on what set?)

@@

TODO: why don't we use F scores or such bullshit?

TODO:Define \(D_j\) as the discrete probability distribution given by \(C_{ij}\) for fixed \(j\).

We then compute the perplexity of the classifier, per given community
$j$, as the exponential of the entropy of the distribution \(D_j\):

\[Ppl_j = e^{-\sum_i C_{ij} log(C_{ij})}\]

\(Ppl_j\) is a measure of the capability (or inability) of the model
to correctly identify a message as coming from a certain
community. (ie. it aggregates confusion on a column of the matrix).

@@

- Correlation between H(c,m) for various models. Identification of specific communities by hand
- Correlation between H(c,m) and Stability(c).

>>>>

\subsection{Losses of CCLM}

% Computation of loss/community/model (show all)
\begin{table}
  \centering
  \begin{tabular}{ccc}
    todo &todo &todo 
  \end{tabular}
  \caption{Model losses per community}
  \label{tab:losses}
\end{table}
TODO commentary. Why are some communities low/high.

\subsection{Analysis of community embeddings}

- PCA plots: not conclusive:

- Correlation with co-occurence matrix (not conclusive)

- Analysis: probably because the model is not using dimensions
with \emph{a priori} equal variance in all dimensions. (Both the LSTM and transformer are highly non-linear complex models)

\subsection{Implicit language-model-based community classifiers}

(TODO: Insert a the correlation plot between two models, on the exponential scale so that it's the same as the other later plots)
TODO: So we can't use the losses directly. Why is this so?

However, we are not so much interested in the ability of the CCLM to
precisely model the language used in a community.

We now turn our interest to language-model-based community classifiers
(LMCC). Given a post $m$, and LMCC gives the probability that it
belongs in a community $c_i$ Using the Bayes theorem, we can turn a
CCLM into a LMCC. Indeed, the probability that a given post $m$
belongs to a community $c_i$ can be calculated as follows:
\[P(c=c_i | m) = P(m | c_i)\frac {P(m)} {P(c=c_i)}\]
In the above,
$P(c=c_i)$ is the frequency of community $c_i$ in the dataset, and
$P(m | c_i)$ is given by the CCLM. $P(m)$ is our normalisation factor, which can be set so that
\[\sum_i P(c=c_i | m) = 1\].

Knowing that $m$ \emph{actually} comes from community $c_j$, we can
measure the the precision our classifier, as a confusion matrix $C$,
which can be calculated as follows for a given set of posts:(TODO: what set exactly?)
\[C_{ij} = average_{m ∈ Posts(c_j)}(P(c=c_i | m))\].

@@

TODO: why don't we use F scores?

While the confusion matrices provide a lot of insight, they are
somewhat \emph{too} fine-grained. For this reason, we will be
interested in confusing the posts from community $c_j$ are to the
LMCC. For this purpose, we consider the perplexity of the LMCC for a
post coming from community $j$, defined as the exponential of the
entropy of the distribution \(D_j\), which is the (discrete)
probability distribution of predicted community for a random post from
$c_j$. $D_j$ is simply the $j$th row in \(C\), and so we obtain the formula:
\[Ppl_j = e^{-\sum_i C_{ij} log(C_{ij})}\]

To recap, \(Ppl_j\) is a measure of the capability (or rather
inability) of the model to correctly identify a message as coming from
a certain community $c_j$.

@@

TODO: show a scatter plot, compute r2, analyse out-of-balance points; discuss why they stand where they do.

Finally, we investigate the correlation between the stability of a
community and the perplexity of the LMCC for it. Stability is defined as TODO.

- computer r2.

We see a positive correlation: this suggests that the more stable a
community is, the more difficult it is to identify posts as coming
from it. What this suggests is that stable communities tend to use a
varied and standard, subset of English, while unstable communities
resort to more formulaic posts. This may suggests that to 'fit' in an
unstable community, one must use more obvious linguistic cues than in
a stable community. In fact, it is reasonable to think that a new
member will ostensibly use community-specifc language, but once
established in a community, a member would tend not to do so.
